Prey skill and behaviour in predator expertise acquisition: insights from a virtual ecosystem

### 2025-08-25 manuscript/manuscript.Rmd
added lay summary

# ABSTRACT {.unnumbered}

@@

# INTRODUCTION {.unnumbered}

@@

>>>>

\newpage
# LAY SUMMARY {.unnumbered}

Predators acquire hunting expertise over successive encouters with their prey, allowing them to be more successful. Using a multiplayer videogame that simulates a predator-prey interaction, we show that the acquisition of predator expertise changes as a function of prey behaviour and skill. Our findings suggest that prey antipredator behaviour could mediate how predators learn and gain skills over time.

\newpage
# ABSTRACT {.unnumbered}

@@

\newpage
# INTRODUCTION {.unnumbered}

@@

# Data availability

The data and code used to produce our analyses are fully available on this GitHub repository: https://github.com/quantitative-ecologist/predator-expertise.
